%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}


%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{https://upa8.github.io}{Pratik Upacharya}}
\end{center}
\vspace{-7mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-9mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:pratikupacharya@gmail.com}{pratikupacharya@gmail.com} ~\textbullet~ \(+91\) 7588948588 ~\textbullet~ \#40, Muktai Nagar,Dhule, Maharashtra, India
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	Selected Projects Section
%---------------------------    -------------------------------------------------------------
\section{Selected Projects}
All projects available on github : \url{https://www.github.com/upa8}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]
\item \textbf{\href{https://github.com/upa8/Autonomous-Robot-Car}{Autonomous Robot Car}} : Implemented multi-threading in python to perform asynchronous 
task like controlling car , obstacle detection , image processing etc simultaneously in background. 
Increased the number of message transfer between raspberry pi and computer by 10 times by implementing websocket over http which further reduces number of tcp connections.
Created android application to control car movements.
Working on and learning machine learning and artificial intelligence to build complete driver less car.

  \item \textbf{\href{https://github.com/upa8/Device-Tracking-System}{Device Tracking System}} - Created a web and android application to track android device at real 
time using background services and GCM. Reduced battery and data usage by 37% by using 
efficient algorithm for background services with timer. Implemented this concept in "Trabus"
android application to find and track buses in city at real time. 
 \item \textbf{\href{http://cupidic.com/}{E-Greeting Cards Platform (Cupidic.com)}} : 
Designed and developed "E-Greeting card" web application to send greetings to friends by customizing predefined templates.Created templates like 3D rotating cube in 3.js with 6 images around each side of cube and one heart shaped animation with flowers. 
\item \textbf{\href{https://github.com/upa8/Thane-Traffic-App}{Thane Traffic App}} : SOS application especially build for women safety in thane . Increased productivity 
and usefulness of application by implementing push notification system to send alert using GCM.
  
\end{itemize}
 
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}
\textbf{Associate Software Engineer, \href{http://www.xoriant.com}{Xoriant, Pune}} \hfill Aug, 2016 - Current\\
Working on projects which include multiple technologies like nodejs, angularJs, MongoDB, Elastic search etc. Also trained on flask and completed one internal project related to room booking. 
\\
\\
\textbf{Full Stack Developer Intern, \href{http://www.twheelo.com}{Twheelo, Nagpur}} \hfill May, 2015 - Current\\
Building a web and android application for renting two wheeler. 
Implemented retrofit library to reduce http connection time by 100 times than in-built Apache http connection in android. 
Working on and learning  angularJs , NodeJs, expressJs , Postgres , Aws , Oauth  etc
\\
\\
\textbf{Technical Coordinator , \href{http://www.polaris2k16.in/}{Polaris2k16, Nagpur}} \hfill Dec, 2015 - March 2016 \\
Build an analytic tool for Polaris event  to manage money collection , user and event information , track expenses , 
generate reports on online event feedback forms.  
Wrote API's to register user through android application.
Wrote efficient scripts to send sms , emails to multiple user with delivery report to resend messages.\\
\\
\textbf{Full Stack Developer Intern, \href{http://www.energylabs.in/}{EnegeryLabs , Nagpur}}
 \hfill June, 2014 - Aug, 2015 \\ 
Leaned android and web development , build one android application "Thane Traffic App" for thane city 
which  launched by Mr. Amitabh Bacchan on 27 feb 2015. 
Build backend web application to manage questions , user answers and admin rating on users answers 
for "whatsyourexcuse.co".
\

%----------------------------------------------------------------------------------------
%	Technical Skills
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\textbf{Languages : }
	Java, Javascript, Pyton, PHP, C, HTML, CSS, Sql \\
\
\textbf{Tools/Frameworks : }
Nodejs, AngularJs,MongoDB,Mocha-Chai, Elastic Search, Android, Git, Mysql,Postgres, Bootstrap, Django, MeteorJS, LaTex, Raspberrypi, OpenCV ,Phonegap, AWS, Matlab, jUnit etc
\	
	
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{itemize}[leftmargin=*]\item
\textbf{B.Tech in Computer Science} \hfill 2012 - 2016 \\
\href{http://rknec.edu}{Ramdeobaba College Of Engineering, Nagpur, India}
  CGPA of \textbf{6.47}/10
\item\textbf{High School} - {Jai Hind Senior College, Dhule} (MSBSHSE) - 78.67\% \hfill 2010 - 2012 \
\item\textbf{Secondary School} - Jai Hind High School, Dhule , Maharashtra (MSBSHSE) - 95.09\% \hfill 2000 - 2010
\end{itemize}
%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements and Awards}
\begin{itemize}[leftmargin=*]
 \item Won gold medal in Hackerrank-Week of code 17 by securing 52nd rank amongst 3576 participants. 
 \item First Runner up in an overnight coding competition in a national event called COMPUFEST held in YCC.
 \item Felicitated by Mr.Amitabh Bacchan and Thane Police for creating android application named 'Thane Traffic 
app'.
\item 
 Conducted a workshop on Android Development for 200 student in RCOEM (Feb 2015)
\end{itemize}

\section{More}
Please visit \href{https://upa8.github.io}{https://upa8.github.io}
\end{resume}
\end{document}



